Stat 400 Project

### 2021-12-06 Stat 400 proj.Rmd
Added bootstrap function

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#testing github
library(tidyverse)

@@

      crucial_distance <- rexp(1, 1/mean_crit_dist)
      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
      # print(c(d <= crucial_distance, x_i, x_s, j, i, nrow(current_infected)))
      if(d <= crucial_distance){
        newly_infected <- c(newly_infected, j)
      }

@@

y <- simulator(30,25,10,10,2,1)
x <- 0:30

library(ggplot2)
ggplot() +
  geom_line(aes(x=x, y=y)) +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')

@@

Plots
``` {r}
ggplot() + 
  geom_line(aes())
```

```{r}
#reported monte carlo summary data
qd = c(0,25,50,75)
pos = c(99.3,99.2,98.7,92.7)
dncpv = c(69,53,46,33)
dncpt = c(26,32,43,42)
r0 = c(1.8,1.73,1.8,1.63)
mcsum = cbind(qd,pos,dncpv,dncpt,r0)
colnames(mcsum,c("Quarantine degree [%]",	"Percentage of size %",	"DNC peak value [cases]",	"DNC peaking time [days]",	"R0"))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#testing github
library(tidyverse)
library(ggplot2)
library(boot)
```

```{r}

@@

      crucial_distance <- rexp(1, 1/mean_crit_dist)

      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
      if(d <= crucial_distance){
        newly_infected <- c(newly_infected, j)
      }

@@

n=100
y <- simulator(n,100,10,10,2,1)
x <- 0:n

ggplot() +
  geom_line(aes(x=x, y=y)) +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')

#bootstrap

mean_func <- function(x, idx) {
  mean(x[idx])
}

daily_cases <- y
boot.case <- boot(daily_cases, mean_func, 2000)

plot(boot.case)

boot.ci(boot.case, conf = .95, type = c("perc", "basic", "norm", "bca"))

@@

```{r}
#reported monte carlo summary data
qd = c(0,25,50,75)
pos = c(99.3,99.2,98.7,92.7)
dncpv = c(69,53,46,33)
dncpt = c(26,32,43,42)
r0 = c(1.8,1.73,1.8,1.63)
mcsum = cbind(qd,pos,dncpv,dncpt,r0)
colnames(mcsum,c("Quarantine degree [%]",	"Percentage of size %",	"DNC peak value [cases]",	"DNC peaking time [days]",	"R0"))
mcsum
```
